---
title: "Lab5"
author: "Mengyu Li"
date: "June 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(stringr)
library(readr)
knitr::opts_chunk$set(echo = TRUE)
```

## Getting Help for Packages

You can see what an entire package has to offer with
```{r}
help(package = "stringr")
```


## Counting number of vowels

Consider the following vector `letrs` which contains various letters:
```{r}
# Garbage string
letrs <- "gfngenodgsyctyviqyyigeinyngbkwjdjqkrrollhpxdkfldlytympmcgmjynihusebtq"
```

If you were to count the number of vowels in `letrs` you would get the following counts:

- a: 0
- e: 3
- i: 4
- o: 2
- u: 1

This exercise will guide you through how to arrive at this frequency table.

```{r}
# Create a character vector of vowels.  Give it an appropriate name.
vowelcharacter <- c("a","e","i","o","u")

# Use str_count to get the counts.  Assign this an appropriate name.
x <- str_count(letrs, vowelcharacter)

# Give each element of the vector a name using the names function.
# The result should look like:
# a e i o u
# 0 3 4 2 1
names(x) <- c("a","e","i","o","u")
x
```

## Exploring new functions: str_pad
Write a short description of what each of the following calls of `str_pad` is doing.  The last three examples were found at the bottom of the function's documentation.

1. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad("a", width = 4, side = "left", pad = "x")
```
It creates an one-element character vector whose minimum width is 4. It puts the string "a" in the character vector and put "x" in the left side of "a" to pad the string.

2. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad("a", width = 3, side = "left")
```
It creates an one-element character vector whose minimum width is 3. It puts the string "a" in the character vector and put " " in the left side of "a" to pad the string.

3. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad(c("a", "abc", "abcdef"), 10)
```
It creates a three-element character vector whose minimum width is 10. It puts the string "a", "abc", "abcdef" in the first, second, and third element in the character vector respectively and put " " in the left side of the strings to pad the vector.

4. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad("a", c(5, 10, 20))
```
It creates a three-element character vector whose minimum width is 5, 10 and 20, respectively. It puts the string "a" in each element in the character vector and put " " in the left side of the strings to pad the vector.

5. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad("a", 10, pad = c("-", "_", " "))
```
It creates a three-element character vector whose minimum width is 10. It puts the string "a" in each element in the character vector and put "-", "_" and " " in the left side of the strings to pad the vector, respectively.




## Regular Expressions

We read in the data from the csv file and extract the names column
```{r}
flags <- read_csv("flags.csv")
countries <- flags$name
```

You may have noticed that in the `countries` vector, words in a country's name are separated by `-`.  Use `str_replace_all` to replace the hyphens with spaces.  For example `"Vatican-City"` should be replaced with `"Vatican City"`

```{r}
# Your code here
str_replace_all(countries, "-", " ")
```

Use `str_detect` to see if there are any countries with the world "island" in them, ignoring case.  You may also want to look up how to use `ignore.case`.

```{r}
# Your code here
any(str_detect(countries, ignore.case("island")))
```

Use `str_subset` to find all countries that begin with a capital `A`.
```{r}
# Your code here
str_subset(countries,"^A")
```

Find all countries that end with `stan`
```{r}
# Your code here
str_subset(countries, ".stan" )
```

Use `str_replace_all` to replace the `$`'s in `baws` with `s`'s.  Recall that the `$` is a metacharacter.
```{r}
baws <- "Bo$$"
str_replace_all(baws, "\\$", "s")
```

Use a character class (denoted by square brackets) to find all countries beginning with a vowel and ending with a consonant.
```{r}
# Fill in
str_subset(countries, "^[AEIOUaeiou].*[^AEIOUaeiou]$")
```




